Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-06 draft.tex
define class of games that satisfy parameter restrictions

\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\ga}{\gamma}
\newcommand{\un}{\underline}
\newcommand{\ov}{\overline}
\newcommand{\de}{\delta}
\linespread{1.05} % Palatino needs more leading (space between lines)
\title{Unrecognized States: A Theory of Self-Determination and Foreign Influence}

@@

\emph{The following are sufficient conditions for such an equilibrium: }

@@

>>>>

\newtheorem{definition}{Definition}
\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\ga}{\gamma}
\newcommand{\un}{\underline}
\newcommand{\ov}{\overline}
\newcommand{\de}{\delta}
\linespread{1.05} % Palatino needs more leading (space between lines)
\title{Unrecognized States: A Theory of Self-Determination and Foreign Influence}

@@

We begin by listing and providing intuition for a set of restrictions on the preferences of the actors and their resources for which we can guarantee that unrecognized statehood is an equilibrium outcome of the repeated game. This set of restrictions identifies a class of games, $\mathcal{G}$:

\begin{definition}
\emph{The class $\mathcal{G}$ includes all those games for which the parameters satisfy the following restrictions:}

@@

\end{enumerate}
\end{definition}
